%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} %Document margins
\usepackage[hidelinks]{hyperref}                                       %Package for hyperlinks without green box 

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Kevin Lamothe}                                                                           %Name
\address{605 Hoka Street, Winnipeg, MB R2C 2V2}                                                %Address
\address{(204)890-6279 \\ klamothe@icloud.com \\ \href{www.kevinlamothe.ca}{kevinlamothe.ca}}  %Phone number, email, website

\begin{document}

% UNCOMMENT FOR A REAL JOB APPLICATION
%----------------------------------------------------------------------------------------
%	CAREER OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
%\begin{rSection}{Objective}
% To continue my personal and career growth with an organization that will allow me to solve challenging engineering problems.
%\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf University of Manitoba, Winnipeg MB} \hfill {2017} 
\\ Bachelor of Science, Electrical Engineering

\end{rSection}
    
%----------------------------------------------------------------------------------------
%	SKILLS  SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    
        Programming & C\#, C\texttt{++} SQL, Matlab, Python \\
        Hardware Design & Cadence CIS, Allegro PCB Designer \\
        Development Tools & Visual Studio, STM32Cube, GIT, JIRA, Confluence \\
        CAD Tools & Solidworks, Solidworks Electrical, AutoCAD \\
    
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
\begin{rSubsection}{Holley Performance Products Canada}{2017 - Present}{Electronics Test Engineer EIT}{}
    
    \item Completed design verification testing of new product development for EFI (electronic fuel injection) applications. Responsible for qualifying new designs with initial electrical in circuit testing, mechanical vibration tests and burn in tests.

    \item Designed analog and digital circuits for functional tests used in manufacturing. Circuits were designed to fully test each product to ensure all inputs and outputs meet designed specifications before final assembly.
    
    \item Completed documentation for product life management cycle. Required defining test specifications, completing bill of material, test fixture wiring and assembly instructions and manufacturing work instructions.

    \item New product development. Completed research on existing products with ageing functionality and components near end of life. Responsible for designing updated products with functions inline with our existing product lineup. Included circuit design, PCB layout, prototyping and qualification testing for releasing to manufacturing.

    \item Software development for manufacturing test applications. Used C\# and the .NET framework to develop WPF applications to deploy device firmware and perform functional tests for mass production. Applications were developed to provide a simple interface and give meaningful feedback to operators on each test step.
    
\end{rSubsection}

\begin{rSubsection}{Manitoba Hydro}{2011 - 2016}{Technical Support - Student}{}

    \item Responsible for project document control using established document management systems. Maintained a construction drawing set and updated with field revisions throughout the project as well as revised drawings from designers and external contractors. 

    \item Conducted project audits to establish work completed against project milestones. Required site visits to document contractor progress across Manitoba to be reported to project stakeholders.
    
\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	AFFILIATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Affiliations}

    {\bf EGM} \hfill {2015 - Present} 

    {\bf IEEE} \hfill {2015 - Present} 
    \\IEEE Canadian Foundation Scholarship Recipient \hfill {2016}

    \end{rSection}

\end{document}